Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-27 be.tex
appendix...

Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{(v_w^2+\sigma_0^2)/\sigma_0}$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.

For a given $\zeta$ we define a critical $\rs/\rsoi=min{
  \frac{frac{7}{2}-\densSlope}{\densSlope \zeta^2, 1}}$ for thermal stability, 
where the first term in the brackets corresponds to twice the value
predicted by equation~\eqref{eq:rsRinf}, in the limit the stellar mass
as $\rs$ is small compared to $\Mbh$. This prescription is somehwat
ad hoc, but...{\bf AG--some motivation...}

Then from equation~\eqref{eq:enthAnal} we may obtain the critical
wind heating parameter $v_{w, \rm crit}/\sigma_{\rm inf}$ for thermal stability as
a function of $\rb/\rsoi$. This is shown in Fig.~\ref{fig:vwCrit}

\begin{figure}
\includegraphics[width=\columnwidth]{vwCrit.pdf}
\caption{\label{fig:vwCrit} Critical heating rate required for thermal
  stability normalized to the velocity dispersion at the sphere
  influence radius, $\sigma_{\rm soi}$ versus $\rb/\rsoi$, the ratio
  of the break radius in the stellar density profile to the sphere of
  influence radius. We assume a core stellar dnsity profile inside of
  $\rb$, so that $\rhostar\sim r^{-1-\Gamma}$ with $\Gamma=0.1$.}
\end{figure}

>>>>

Recall that $\rs$ the stagnation radius, $x\equiv r/\rs$, $\zeta=\sqrt{v_w^2+\sigma_0^2}/\sigma_0$, $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.

For sufficiently large radii ($x$), the expression above always
becomes negative, which means that a break in the stellar density
profile is necessary in order to obtain an outflow. For a given
$\rb/\rsoi$ there is a critical $\zeta$, $\zeta_{c}$, such that if
$\zeta>\zeta_c$, an outflow will be possible from any
radius. On the other hand if $\zeta<\zeta_c$, then there is a
minimum radius from which an outflow is possible, so that we have a
constraint on $\rs/\rsoi$.

For cusp galaxies ($\Gamma$=0.8), $\zeta_c\simeq \sqrt 2$
($v_w\simeq\sigma_0$).  On the other hand for core galaxies
($\Gamma$=0.1) we find $\zeta_c\simeq (\rb/\rsoi)^{0.45}$. We also
find that for core galaxies for $\zeta<\zeta_c$, there is a minimum
for $\rs/\rsoi$, $\left(\rs/\rsoi\right)_{\rm min}$--if $\rs/\rsoi$ were
less than this value the gas enthalpy would become negative inside of
the break radius which is clearly unphysical.  This may be roughly
approximated using (see Fig.~\ref{fig:rbRinf})

\begin{align}
&\left.\frac{\rs}{\rsoi}\right|_{\rm min}=\frac{\rb}{\rsoi} \frac{\sqrt{\zeta_c-\zeta}}{\sqrt{\zeta_c-1}}\nonumber\\
&\zeta_c\simeq \frac{\rb}{\rsoi}^{0.45}
\label{eq:rsRinfCrit}
\end{align}

\begin{figure}
\includegraphics[width=\columnwidth]{rbRinf.pdf}
\caption{\label{fig:rbRinf} Mininmum value for ratio of the stagnation
  radius to the influence radius, $\rs/\rsoi$ for core galaxies
  ($\Gamma=0.1$) derived by requiring enthalpy of the gas to remain
  positive out to the break radius $\rb$. The solid lines correspond
  to the constraint computed numerically from
  equation~\eqref{eq:enthAnal}, while the dashed line correspond the
  results of the fitting formula equation~\eqref{eq:rsRinfCrit}. The
  x-intercept of each curve corresponds to the critical $\zeta$,
  $\zeta_c$ above which an outflow is possible from any radius}
\end{figure}
